---
title: "Sexual Violence Main"
author: "Jakob Aggers"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    number_sections: true
    toc: yes
    toc_depth: 3
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '3'
editor_options: 
  markdown: 
    wrap: 72
---

## Packages
```{r}
library(tidyverse)
library(readxl)
library(forcats)
library(ezids)
```

## Load Data
```{r}
#acled_sexual_violence <- read_csv("../Data/acled_sexual_violence.csv", name_repair = "universal")

SVAC <- read_excel("../Data/SVAC_3.2_conflictyears.xlsx")

SVAC_complete <- read_excel("../Data/SVAC_3.2_complete.xlsx")

```

## Data Cleaning
### SVAC
```{r}
##############  SVAC  ############## 
SVAC <- SVAC %>%
  mutate(
    form_rape = ifelse(grepl("1", form), 1, 0),
    form_sexual_slavery = ifelse(grepl("2", form), 1, 0),
    form_forced_prostitution = ifelse(grepl("3", form), 1, 0),
    form_forced_pregnancy = ifelse(grepl("4", form), 1, 0),
    form_forced_sterilization_abortion = ifelse(grepl("5", form), 1, 0),
    form_sexual_mutilation = ifelse(grepl("6", form), 1, 0),
    form_sexual_torture = ifelse(grepl("7", form), 1, 0)
  )

SVAC <- SVAC %>% 
  select(!form)

SVAC <- SVAC %>%
  mutate(overall_prev = pmax(state_prev, hrw_prev, ai_prev))

SVAC <- SVAC %>%
  mutate(
    actor_type = case_when(
      actor_type == "1" ~ "State government",
      actor_type == "2" ~ "State supporting state",
      actor_type == "3" ~ "Rebel group",
      actor_type == "4" ~ "State supporting rebel group",
      actor_type == "5" ~ "Secondary state (side B)",
      actor_type == "6" ~ "Pro-government militias (PGMs)"
    ),
    type_of_conflict = case_when(
      type_of_conflict == "2" ~ "Interstate Conflict",
      type_of_conflict == "3" ~ "Intrastate Conflict",
      type_of_conflict == "4" ~ "Internationalized Internal Armed Conflict"
    ),
    incompatibility = case_when(
      incompatibility == "0" ~ "None",
      incompatibility == "1" ~ "Territory",
      incompatibility == "2" ~ "Government",
      incompatibility == "3" ~ "Government and Territory"
    ),
    region = case_when(
      region == "1" ~ "Europe",
      region == "2" ~ "Middle East",
      region == "3" ~ "Asia",
      region == "4" ~ "Africa",
      region == "5" ~ "Americas"
    ),
    postc = case_when(
      postc == "0" ~ "Otherwise",
      postc == "1" ~ "Post conflict"
    ),
    conflictyear = case_when(
      conflictyear == "0" ~ "Not in active conflict",
      conflictyear == "1" ~ "In active conflict"
    ),
    interm = case_when(
      interm == "0" ~ "Not within an interim conflict period",
      interm == "1" ~ "Within an interim conflict period"
    ),
     )

SVAC$overall_prev <- factor(SVAC$overall_prev, levels = c(0, 1, 2, 3),
                            labels = c("Sexual violence not present", "Overall Prevalence: Low", 
                                       "Overall Prevalence: Medium", "Overall Prevalence: High"))

SVAC <- SVAC %>% 
  mutate(actor_type = as_factor(actor_type),
         type_of_conflict = as_factor(type_of_conflict),
         incompatibility = as_factor(incompatibility),
         region = as_factor(region),
         conflictyear = as_factor(conflictyear),
         region = as_factor(region),
         conflictyear = as_factor(conflictyear),
         interm = as_factor(interm),
         postc = as_factor(postc),
         actorid = as_factor(actorid))


SVAC <- SVAC %>% 
  filter(!overall_prev == "-99")

filtered_SVAC <- SVAC %>%
  filter(overall_prev != "Sexual violence not present")

SVAC<- SVAC %>%
  mutate(prev_binary = if_else(overall_prev == "Sexual violence not present", "Not Prevalent", "Prevalent"))

```

### SVAC Complete
```{r}
SVAC_complete <- SVAC_complete %>%
  mutate(
    form_rape = ifelse(grepl("1", form), 1, 0),
    form_sexual_slavery = ifelse(grepl("2", form), 1, 0),
    form_forced_prostitution = ifelse(grepl("3", form), 1, 0),
    form_forced_pregnancy = ifelse(grepl("4", form), 1, 0),
    form_forced_sterilization_abortion = ifelse(grepl("5", form), 1, 0),
    form_sexual_mutilation = ifelse(grepl("6", form), 1, 0),
    form_sexual_torture = ifelse(grepl("7", form), 1, 0)
  )

SVAC_complete <- SVAC_complete %>% 
  select(!form)

SVAC_complete <- SVAC_complete %>%
  mutate(overall_prev = pmax(state_prev, hrw_prev, ai_prev))

SVAC_complete <- SVAC_complete %>%
  mutate(
    actor_type = case_when(
      actor_type == "1" ~ "State government",
      actor_type == "2" ~ "State supporting state",
      actor_type == "3" ~ "Rebel group",
      actor_type == "4" ~ "State supporting rebel group",
      actor_type == "5" ~ "Secondary state (side B)",
      actor_type == "6" ~ "Pro-government militias (PGMs)"
    ),
    type = case_when(
      type == "2" ~ "Interstate Conflict",
      type == "3" ~ "Intrastate Conflict",
      type == "4" ~ "Internationalized Internal Armed Conflict"
    ),
    incomp = case_when(
      incomp == "0" ~ "None",
      incomp == "1" ~ "Territory",
      incomp == "2" ~ "Government",
      incomp == "3" ~ "Government and Territory"
    ),
    region = case_when(
      region == "1" ~ "Europe",
      region == "2" ~ "Middle East",
      region == "3" ~ "Asia",
      region == "4" ~ "Africa",
      region == "5" ~ "Americas"
    ),
    postc = case_when(
      postc == "0" ~ "Otherwise",
      postc == "1" ~ "Post conflict"
    ),
    conflictyear = case_when(
      conflictyear == "0" ~ "Not in active conflict",
      conflictyear == "1" ~ "In active conflict"
    ),
    interm = case_when(
      interm == "0" ~ "Not within an interim conflict period",
      interm == "1" ~ "Within an interim conflict period"
    ),
     )

SVAC_complete$overall_prev <- factor(SVAC_complete$overall_prev, levels = c(0, 1, 2, 3),
                            labels = c("Sexual violence not present", "Overall Prevalence: Low", 
                                       "Overall Prevalence: Medium", "Overall Prevalence: High"))

SVAC_complete <- SVAC_complete %>% 
  mutate(actor_type = as_factor(actor_type),
         type = as_factor(type),
         incomp = as_factor(incomp),
         region = as_factor(region),
         conflictyear = as_factor(conflictyear),
         region = as_factor(region),
         conflictyear = as_factor(conflictyear),
         interm = as_factor(interm),
         postc = as_factor(postc),
         actorid = as_factor(actorid))


SVAC_complete <- SVAC_complete %>% 
  filter(!overall_prev == "-99")

filtered_SVAC_complete <- SVAC_complete %>%
  filter(overall_prev != "Sexual violence not present")

SVAC_complete <- SVAC_complete %>%
  mutate(prev_binary = if_else(overall_prev == "Sexual violence not present", "Not Prevalent", "Prevalent"))

```


### ACLED
```{r}
##############  ACLED  ##############  
acled_sexual_violence <- 
  acled_sexual_violence %>%
  mutate(Actor_Type = case_when(
    inter1 == 1 ~ "State Actor",
    inter1 == 2 ~ "Rebel Group",
    inter1 == 3 ~ "Political Militias",
    inter1 == 4 ~ "Identity Militias",
    inter1 == 5 ~ "Rioters",
    inter1 == 6 ~ "Protesters",
    inter1 == 7 ~ "Civilians",
    inter1 == 8 ~ "External/Other Forces",
    TRUE ~ NA_character_  
  ))


acled_sexual_violence %>% 
  group_by(Actor_Type) %>% 
  summarize(n = n())
# to many individual civilian actions, remove them

acled_sexual_violence <- 
  acled_sexual_violence %>% 
  filter(Actor_Type != "Civilians")

```

## EDA

### EDA for SVAC (During Conflict)

#### Hisograms and Line Graphs for Overall_prev
```{r}
# Histogram by Year
ggplot(SVAC, aes(x = year)) +
  geom_histogram(binwidth = 1, fill = "skyblue", color = "black") +
  theme_minimal() +
  labs(title = "Distribution of Observations by Year", x = "Year", y = "Count") +
  theme(plot.title = element_text(hjust = 0.5))


# Histogram by year by overall prev
SVAC %>%
  ggplot(aes(x = year, fill = overall_prev)) +
  geom_histogram(binwidth = 1, position = "stack", alpha = 0.7) +
  scale_fill_manual(values = c("Sexual violence not present" = "skyblue",
                   "Overall Prevalence: Low" = "yellow",
                   "Overall Prevalence: Medium" = "orange",
                   "Overall Prevalence: High" = "red")) +
  theme_minimal() +
  labs(title = "Distribution of Years by Overall Prevalence",
       x = "Year",
       y = "Count",
       fill = "Overall Prevalence") +
  theme(plot.title = element_text(hjust = 0.5))


# Histogram by year by overall prev without 0's
filtered_SVAC %>%
  ggplot(aes(x = year, fill = overall_prev)) +
  geom_histogram(binwidth = 1, position = "stack", alpha = 0.7) +
  scale_fill_manual(values = c("Overall Prevalence: Low" = "yellow",
                   "Overall Prevalence: Medium" = "orange",
                   "Overall Prevalence: High" = "red")) +
  theme_minimal() +
  labs(title = "Distribution of Years by Overall Prevalence",
       x = "Year",
       y = "Count",
       fill = "Overall Prevalence") +
  theme(plot.title = element_text(hjust = 0.5))


 #### Now Line graphs
summary_SVAC <- SVAC %>%
  group_by(year, overall_prev) %>%
  summarise(count = n(), .groups = 'drop')

ggplot(summary_SVAC, aes(x = year, y = count, color = overall_prev, group = overall_prev)) +
  geom_line() +
  theme_minimal() +
  labs(title = "Prevalence of Sexual Violence in Conflict by Year (including not present)",
       x = "Year",
       y = "Count",
       color = "Prevalence Category") +
  theme(plot.title = element_text(hjust = 0.5))

ggsave("../Images/SVAC by overall_prev including not present.png", width  = 6, height = 4, units = "in")

# SVAC filtered
summary_data_filtered <- filtered_SVAC %>%
  group_by(year, overall_prev) %>%
  summarise(count = n(), .groups = 'drop')

ggplot(summary_data_filtered, aes(x = year, y = count, color = overall_prev, group = overall_prev)) +
  geom_line() +
  theme_minimal() +
  labs(title = "Prevalence of Sexual Violence in Conflict by Year",
       x = "Year",
       y = "Count",
       color = "Prevalence Category") +
  theme(plot.title = element_text(hjust = 0.5))

ggsave("../Images/SVAC by overall_prev (filter prevalent).png", width  = 6, height = 4, units = "in")
```


#### Charts for Distribution of Other Variables

```{r}
# Actor Type
ggplot(SVAC, aes(x = actor_type)) +
  geom_bar(fill = "lightgreen", color = "black") +
  theme_minimal() +
  labs(title = "Distribution of Actor Types", x = "Actor Type", y = "Count") +
  theme(plot.title = element_text(hjust = 0.5), 
        axis.text.x = element_text(angle = 45, hjust = 1))

#actor type + overall_prev 
ggplot(SVAC, aes(x = actor_type, fill = overall_prev)) +
  geom_bar(color = "black") +
  scale_fill_manual(values = c("Sexual violence not present" = "lightblue",
                                "Overall Prevalence: Low" = "yellow",
                                "Overall Prevalence: Medium" = "orange",
                                "Overall Prevalence: High" = "red")) +
  theme_minimal() +
  labs(title = "Distribution of Actor Types by Overall Prevalence", 
       x = "Type of Conflict", y = "Count") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 45, hjust = 1))


#actor type + overall_prev without prev = 0
ggplot(filtered_SVAC, aes(x = actor_type, fill = overall_prev)) +
  geom_bar(color = "black") +
  scale_fill_manual(values = c("Overall Prevalence: Low" = "yellow",
                                "Overall Prevalence: Medium" = "orange",
                                "Overall Prevalence: High" = "red")) +
  theme_minimal() +
  labs(title = "Distribution of Actor Types by Overall Prevalence", 
       x = "Type of Conflict", y = "Count") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 45, hjust = 1))

# Type of Conflict
ggplot(SVAC, aes(x = type_of_conflict)) +
  geom_bar(fill = "lightcoral", color = "black") +
  theme_minimal() +
  labs(title = "Distribution of Conflict Types", x = "Type of Conflict", y = "Count") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 45, hjust = 1))

#region
ggplot(SVAC, aes(x = region)) +
  geom_bar(fill = "lightblue", color = "black") +
  theme_minimal() +
  labs(title = "Distribution of Conflict Regions", x = "Type of Conflict", y = "Count") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 45, hjust = 1))

#region + overall_prev
ggplot(SVAC, aes(x = region, fill = overall_prev)) +
  geom_bar(color = "black") +
  scale_fill_manual(values = c("Sexual violence not present" = "lightblue",
                                "Overall Prevalence: Low" = "yellow",
                                "Overall Prevalence: Medium" = "orange",
                                "Overall Prevalence: High" = "red")) +
  theme_minimal() +
  labs(title = "Distribution of Conflict Regions by Overall Prevalence", 
       x = "Type of Conflict", y = "Count") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 45, hjust = 1))

#region + overall_prev without prev = 0
ggplot(filtered_SVAC, aes(x = region, fill = overall_prev)) +
  geom_bar(color = "black") +
  scale_fill_manual(values = c("Overall Prevalence: Low" = "yellow",
                                "Overall Prevalence: Medium" = "orange",
                                "Overall Prevalence: High" = "red")) +
  theme_minimal() +
  labs(title = "Distribution of Conflict REgions by Overall Prevalence", 
       x = "Type of Conflict", y = "Count") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 45, hjust = 1))
```

### EDA for SVAC (Complete)

#### Hisograms and Line Graphs for Overall_prev

```{r}
# Histogram by Year
ggplot(SVAC_complete, aes(x = year)) +
  geom_histogram(binwidth = 1, fill = "skyblue", color = "black") +
  theme_minimal() +
  labs(title = "Distribution of Observations by Year (Complete)", x = "Year", y = "Count") +
  theme(plot.title = element_text(hjust = 0.5))


# Histogram by year by overall prev
SVAC_complete %>%
  ggplot(aes(x = year, fill = overall_prev)) +
  geom_histogram(binwidth = 1, position = "stack", alpha = 0.7) +
  scale_fill_manual(values = c("Sexual violence not present" = "skyblue",
                   "Overall Prevalence: Low" = "yellow",
                   "Overall Prevalence: Medium" = "orange",
                   "Overall Prevalence: High" = "red")) +
  theme_minimal() +
  labs(title = "Distribution of Years by Overall Prevalence (Complete)",
       x = "Year",
       y = "Count",
       fill = "Overall Prevalence") +
  theme(plot.title = element_text(hjust = 0.5))


# Histogram by year by overall prev without 0's
filtered_SVAC_complete %>%
  ggplot(aes(x = year, fill = overall_prev)) +
  geom_histogram(binwidth = 1, position = "stack", alpha = 0.7) +
  scale_fill_manual(values = c("Overall Prevalence: Low" = "yellow",
                   "Overall Prevalence: Medium" = "orange",
                   "Overall Prevalence: High" = "red")) +
  theme_minimal() +
  labs(title = "Distribution of Years by Overall Prevalence (Complete)",
       x = "Year",
       y = "Count",
       fill = "Overall Prevalence") +
  theme(plot.title = element_text(hjust = 0.5))


#### Now Line graphs
summary_SVAC_complete <- SVAC_complete %>%
  group_by(year, overall_prev) %>%
  summarise(count = n(), .groups = 'drop')

ggplot(summary_SVAC_complete, aes(x = year, y = count, color = overall_prev, group = overall_prev)) +
  geom_line() +
  theme_minimal() +
  labs(title = "Prevalence of Sexual Violence in Conflict by Year including not present (Complete)",
       x = "Year",
       y = "Count",
       color = "Prevalence Category") +
  theme(plot.title = element_text(hjust = 0.5))

# SVAC_complete filtered
summary_data_filtered_complete <- filtered_SVAC_complete %>%
  group_by(year, overall_prev) %>%
  summarise(count = n(), .groups = 'drop')

ggplot(summary_data_filtered_complete, aes(x = year, y = count, color = overall_prev, group = overall_prev)) +
  geom_line() +
  theme_minimal() +
  labs(title = "Prevalence of Sexual Violence in Conflict by Year (Complete)",
       x = "Year",
       y = "Count",
       color = "Prevalence Category") +
  theme(plot.title = element_text(hjust = 0.5))

```

#### Other Distributions
```{r}
# Actor Type
ggplot(SVAC_complete, aes(x = actor_type)) +
  geom_bar(fill = "lightgreen", color = "black") +
  theme_minimal() +
  labs(title = "Distribution of Actor Types (Complete)", x = "Actor Type", y = "Count") +
  theme(plot.title = element_text(hjust = 0.5), 
        axis.text.x = element_text(angle = 45, hjust = 1))

#actor type + overall_prev 
ggplot(SVAC_complete, aes(x = actor_type, fill = overall_prev)) +
  geom_bar(color = "black") +
  scale_fill_manual(values = c("Sexual violence not present" = "lightblue",
                                "Overall Prevalence: Low" = "yellow",
                                "Overall Prevalence: Medium" = "orange",
                                "Overall Prevalence: High" = "red")) +
  theme_minimal() +
  labs(title = "Distribution of Actor Types by Overall Prevalence (Complete)", 
       x = "Type of Conflict", y = "Count") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 45, hjust = 1))


#actor type + overall_prev without prev = 0
ggplot(filtered_SVAC_complete, aes(x = actor_type, fill = overall_prev)) +
  geom_bar(color = "black") +
  scale_fill_manual(values = c("Overall Prevalence: Low" = "yellow",
                                "Overall Prevalence: Medium" = "orange",
                                "Overall Prevalence: High" = "red")) +
  theme_minimal() +
  labs(title = "Distribution of Actor Types by Overall Prevalence (Complete)", 
       x = "Type of Conflict", y = "Count") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 45, hjust = 1))

# Type of Conflict
ggplot(SVAC_complete, aes(x = type)) +
  geom_bar(fill = "lightcoral", color = "black") +
  theme_minimal() +
  labs(title = "Distribution of Conflict Types (Complete)", x = "Type of Conflict", y = "Count") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 45, hjust = 1))

#region
ggplot(SVAC_complete, aes(x = region)) +
  geom_bar(fill = "lightblue", color = "black") +
  theme_minimal() +
  labs(title = "Distribution of Conflict Regions (Complete)", x = "Type of Conflict", y = "Count") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 45, hjust = 1))

#region + overall_prev
ggplot(SVAC_complete, aes(x = region, fill = overall_prev)) +
  geom_bar(color = "black") +
  scale_fill_manual(values = c("Sexual violence not present" = "lightblue",
                                "Overall Prevalence: Low" = "yellow",
                                "Overall Prevalence: Medium" = "orange",
                                "Overall Prevalence: High" = "red")) +
  theme_minimal() +
  labs(title = "Distribution of Conflict Regions by Overall Prevalence (Complete)", 
       x = "Type of Conflict", y = "Count") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 45, hjust = 1))

#region + overall_prev without prev = 0
ggplot(filtered_SVAC_complete, aes(x = region, fill = overall_prev)) +
  geom_bar(color = "black") +
  scale_fill_manual(values = c("Overall Prevalence: Low" = "yellow",
                                "Overall Prevalence: Medium" = "orange",
                                "Overall Prevalence: High" = "red")) +
  theme_minimal() +
  labs(title = "Distribution of Conflict Regions by Overall Prevalence (Complete)", 
       x = "Type of Conflict", y = "Count") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 45, hjust = 1))

#conflict year
ggplot(SVAC_complete, aes(x = conflictyear)) +
  geom_bar(fill = "lightgreen", color = "black") +
  theme_minimal() +
  labs(title = "Distribution of conflictyear (Complete)", x = "conflictyear", y = "Count") +
  theme(plot.title = element_text(hjust = 0.5), 
        axis.text.x = element_text(angle = 45, hjust = 1))

# postc
ggplot(SVAC_complete, aes(x = postc)) +
  geom_bar(fill = "lightgreen", color = "black") +
  theme_minimal() +
  labs(title = "Distribution of postc (Complete)", x = "postc", y = "Count") +
  theme(plot.title = element_text(hjust = 0.5), 
        axis.text.x = element_text(angle = 45, hjust = 1))

#interm
ggplot(SVAC_complete, aes(x = interm)) +
  geom_bar(fill = "lightgreen", color = "black") +
  theme_minimal() +
  labs(title = "Distribution of interm (Complete)", x = "interm", y = "Count") +
  theme(plot.title = element_text(hjust = 0.5), 
        axis.text.x = element_text(angle = 45, hjust = 1))

SVAC_complete %>% 
  group_by(conflictyear, postc, interm) %>% 
  summarize(n = n())
```

### EDA for ACLED
```{r}
ggplot(acled_sexual_violence, aes(x = year)) +
  geom_histogram(binwidth = 1, fill = "salmon", color = "black") +
  theme_minimal() +
  labs(title = "ACLED Distribution of Observations by Year (Complete)", x = "Year", y = "Count") +
  theme(plot.title = element_text(hjust = 0.5))


acled_sexual_violence %>% 
  group_by(Actor_Type) %>% 
  summarize(n = n())

summary_acled <- acled_sexual_violence %>%
  group_by(year, Actor_Type) %>%
  summarise(count = n(), .groups = 'drop')

ggplot(summary_acled, aes(x = year, y = count, color = Actor_Type, group = Actor_Type)) +
  geom_line() +
  theme_minimal() +
  labs(title = "ACLED Actor Type Prevalence by Year",
       x = "Year",
       y = "Count",
       color = "Prevalence Category") +
  theme(plot.title = element_text(hjust = 0.5))

(ggsave("../Images/ACLED Frequency by Actor Type.png", width  = 6, height = 4, units = "in"))

acled_sexual_violence %>% 
  group_by(region, Actor_Type) %>% 
  summarize(n = n()) %>% 
  arrange(desc(n))

acled_sexual_violence %>% 
  group_by(region) %>% 
  summarize(n = n()) %>% 
  arrange(desc(n))
```

## Chi Squared

### Chi Squared SVAC

```{r chisq}
# region
region_ranktable = xtabs(~ overall_prev + region, data = SVAC)

chisqres_region = chisq.test(region_ranktable)
chisqres_region

# actor_type
actor_type_ranktable = xtabs(~ overall_prev + actor_type, data = SVAC)

chisqres_actor_type = chisq.test(actor_type_ranktable)
chisqres_actor_type

# incompatibility
incompatibility_ranktable = xtabs(~ overall_prev + incompatibility, data = SVAC)

chisqres_incompatibility = chisq.test(incompatibility_ranktable)
chisqres_incompatibility 

# type_of_conflict
type_of_conflict_ranktable = xtabs(~ overall_prev + type_of_conflict, data = SVAC)

chisqres_type_of_conflict = chisq.test(type_of_conflict_ranktable)
chisqres_type_of_conflict 

chisqres_SVAC_results <- data.frame(
  Variable = c("Region", "Actor Type", "Incompatibility", "Type of Conflict"),
  ChiSquared = c(chisqres_region$statistic, chisqres_actor_type$statistic, chisqres_incompatibility$statistic, chisqres_type_of_conflict$statistic),
  DegreesOfFreedom = c(chisqres_region$parameter, chisqres_actor_type$parameter, chisqres_incompatibility$parameter, chisqres_type_of_conflict$parameter),
  P_Value = c(chisqres_region$p.value, chisqres_actor_type$p.value, chisqres_incompatibility$p.value, chisqres_type_of_conflict$p.value),
  WarningMessage = c(FALSE, TRUE, TRUE, TRUE), # Manually indicate warning messages
  Independence = c(chisqres_region$p.value < 0.05, chisqres_actor_type$p.value < 0.05, chisqres_incompatibility$p.value < 0.05, chisqres_type_of_conflict$p.value < 0.05)
)

chisqres_SVAC_results

acled_region_actor_ranktable = xtabs(~ region + actor_type, data = SVAC)

chisqres_acled_region_actor = chisq.test(acled_region_actor_ranktable)
chisqres_acled_region_actor 
```
### Chi Squared SVAC Complete

```{r}
# conflictyear
conflictyear_ranktable = xtabs(~ overall_prev + conflictyear, data = SVAC_complete)

chisqres_conflictyear = chisq.test(conflictyear_ranktable)
chisqres_conflictyear

# interm
interm_ranktable = xtabs(~ overall_prev + interm, data = SVAC_complete)

chisqres_interm = chisq.test(interm_ranktable)
chisqres_interm

# postc
postc_ranktable = xtabs(~ overall_prev + postc, data = SVAC_complete)

chisqres_postc = chisq.test(postc_ranktable)
chisqres_postc


chisqres_SVAC_complete_results <- data.frame(
  Variable = c("Conflictyear", "Interm", "Postc"),
  ChiSquared = c(chisqres_conflictyear$statistic, chisqres_interm$statistic, chisqres_postc$statistic),
  DegreesOfFreedom = c(chisqres_conflictyear$parameter, chisqres_interm$parameter, chisqres_postc$parameter),
  PValue = c(chisqres_conflictyear$p.value, chisqres_interm$p.value, chisqres_postc$p.value),
  WarningMessage = c(FALSE, FALSE, FALSE), # No warning messages provided
  Independence = c(chisqres_conflictyear$p.value < 0.05, chisqres_interm$p.value < 0.05, chisqres_postc$p.value < 0.05)
)

chisqres_SVAC_complete_results
```


### Chi Squared ACLED
```{r}
actor_region_ranktable = xtabs(~ Actor_Type + region, data = acled_sexual_violence)
actor_region_ranktable

chisqres_actor_region = chisq.test(actor_region_ranktable)
chisqres_actor_region

chisqres_acled_results <- data.frame(
  Variable = c("Actor Region"),
  ChiSquared = chisqres_actor_region$statistic,
  DegreesOfFreedom = chisqres_actor_region$parameter,
  PValue = chisqres_actor_region$p.value,
  WarningMessage = TRUE,
  Independence = chisqres_actor_region$p.value < 0.05
)

chisqres_acled_results
```

## Vizualizations
```{r}
# interim, postc, and conflictyear
SVAC_complete_prev <- SVAC_complete %>% 
  filter(prev_binary == "Prevalent")


# Create the plot for conflictyear
ggplot(SVAC_complete_prev, aes(x = year, color = conflictyear)) +
  geom_line(stat = "count") +
  scale_color_discrete() +
  labs(x = "Year", y = "Frequency", title = "Frequency of Prevalent by Conflict Year") +
  theme_minimal()

ggsave(ggsave("../Images/Frequency by Conflict Year.png", width  = 6, height = 4, units = "in"))

# Create the plot for postc
ggplot(SVAC_complete_prev, aes(x = year, color = postc)) +
  geom_line(stat = "count") +
  scale_color_discrete() +
  labs(x = "Year", y = "Frequency", title = "Frequency of Prevalent by Post Conflict") +
  theme_minimal()

ggsave(ggsave("../Images/Frequency by PostConflict.png", width  = 6, height = 4, units = "in"))

# Create the plot for interm
ggplot(SVAC_complete_prev, aes(x = year, color = interm)) +
  geom_line(stat = "count") +
  scale_color_discrete() +
  labs(x = "Year", y = "Frequency", title = "Frequency of Prevalent by Interim") +
  theme_minimal()

ggsave(ggsave("../Images/Frequency by Interim.png", width  = 6, height = 4, units = "in"))
```

### 100% graphs

```{r}
# within prev, region x actor type
filtered_SVAC %>%
  count(region, actor_type) %>%
  group_by(region) %>%
  mutate(percentage = n / sum(n)) %>%
  ggplot(aes(x = region, y = percentage, fill = actor_type)) +
  geom_bar(stat = "identity", position = "fill") +
  labs(y = "Percentage", x = "Region", fill = "Actor Type") +
  theme_minimal() +
  ggtitle("100% Stacked Bar Chart of Actor Type by Region") +
  scale_fill_manual(values = c("#1f77b4", "#ff7f0e", "#2ca02c", "#d62728", "#9467bd", "#8c564b", "#e377c2", "#7f7f7f", "#bcbd22", "#17becf"))

ggsave(ggsave("../Images/Region bar by actor.png", width  = 6, height = 4, units = "in"))

# within prev, region x overall_prev
filtered_SVAC %>%
  count(region, overall_prev) %>%
  group_by(region) %>%
  mutate(percentage = n / sum(n)) %>%
  ggplot(aes(x = region, y = percentage, fill = overall_prev)) +
  geom_bar(stat = "identity", position = "fill") +
  labs(y = "Percentage", x = "Region", fill = "Overall Prevalence") +
  theme_minimal() +
  ggtitle("100% Stacked Bar Chart of Overall Prevalence by Region") +
  scale_fill_manual(values = c("darkgoldenrod1", "darkorange", "red"))

ggsave(ggsave("../Images/Region bar by prevalence.png", width  = 6, height = 4, units = "in"))

# within prev, region x type
filtered_SVAC %>% 
  count(region, type_of_conflict) %>%
  group_by(region) %>%
  mutate(percentage = n / sum(n)) %>%
  ggplot(aes(x = region, y = percentage, fill = type_of_conflict)) +
  geom_bar(stat = "identity", position = "fill") +
  labs(y = "Percentage", x = "Region", fill = "Conflict Type") +
  theme_minimal() +
  ggtitle("100% Stacked Bar Chart of Conflict Type by Region") +
  scale_fill_manual(values = c("lightblue", "blue", "navy"))

ggsave(ggsave("../Images/Region bar by conflict type.png", width  = 6, height = 4, units = "in"))

# Within prev, region x type (not added to 100%)

ggplot(SVAC_complete, aes(x = actor_type, fill = overall_prev)) +
  geom_bar(color = "black") +
  scale_fill_manual(values = c("Sexual violence not present" = "lightblue",
                                "Overall Prevalence: Low" = "yellow",
                                "Overall Prevalence: Medium" = "orange",
                                "Overall Prevalence: High" = "red")) +
  theme_minimal() +
  labs(title = "Distribution of Actor Types by Overall Prevalence (Complete)", 
       x = "Type of Conflict", y = "Count") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(filtered_SVAC, aes(x = region, fill = type_of_conflict)) +
  geom_bar(color = "black") +
  labs(y = "Count", x = "Region", fill = "Conflict Type") +
  theme_minimal() +
  ggtitle("Bar Chart of Conflict Type by Region") +
  scale_fill_manual(values = c("lightblue", "blue", "navy"))

ggsave(ggsave("../Images/Region bar by conflict type (not 100%).png", width  = 6, height = 4, units = "in"))

# within prev, region x incompatibility
filtered_SVAC %>% 
  count(region, incompatibility) %>%
  group_by(region) %>%
  mutate(percentage = n / sum(n)) %>%
  ggplot(aes(x = region, y = percentage, fill = incompatibility)) +
  geom_bar(stat = "identity", position = "fill") +
  labs(y = "Percentage", x = "Region", fill = "Incompatibility") +
  theme_minimal() +
  ggtitle("100% Stacked Bar Chart of iIncompatibility Type by Region") +
  scale_fill_manual(values = c("aquamarine3", "darkolivegreen3", "darkgreen"))

ggsave(ggsave("../Images/Region bar by incompatibility.png", width  = 6, height = 4, units = "in"))


# line graph for Africa
filtered_SVAC %>% 
  filter(region == "Africa") %>% 
  ggplot(aes(x = year, color = actor_type)) +
  geom_line(stat = "count") +
  scale_color_discrete() +
  labs(x = "Year", y = "Frequency", title = "Frequency of Instances within Africa by Actor") +
  theme_minimal()

ggsave("../Images/Actor Type Line Graph Africa.png", width  = 6, height = 4, units = "in")

#conflict type Africa
filtered_SVAC %>% 
  filter(region == "Africa") %>% 
  ggplot(aes(x = year, color = type_of_conflict)) +
  geom_line(stat = "count") +
  scale_color_discrete() +
  labs(x = "Year", y = "Frequency", title = "Frequency of Instances within Africa by Conflict Type") +
  theme_minimal()

ggsave("../Images/Conflict Type Line Graph Africa.png", width  = 6, height = 4, units = "in")

```


